03 Data Vizualization

### 2022-04-06 03_data_viz.Rmd
re-did bacdive FA plots

## Phyla FA profiles

```{r}
p_tax_FA <- fatty_acids_wide_with_tax %>% 
  select(-ID) %>% 
  # Remove Fungi from this plot
  filter(phylum != "Fungi") %>% 
  pivot_longer(cols = -phylum, 
               names_to = "FA",
               values_to = "rel_abund") %>%
  ggplot(aes(x = FA, 
             y = rel_abund,
             color = phylum)) +
  #stat_pointinterval(point_interval = "mean_qi") +
  geom_boxplot(
    outlier.shape = NA,
    alpha = 0.1
    ) +
  facet_wrap(vars(phylum), nrow = 1) +
  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
  labs(y = "Relative Abundance",
       x = "",
       color = "Phylum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1),
        panel.grid = element_blank(),
        strip.background = element_blank(),
        legend.position = "NA",
        strip.text = element_text(size = 16)
        # legend.background = element_rect(
        #                           size=0.5, 
        #                           linetype="solid", 
        #                           colour ="black")
        )

# cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
#           plot = p_tax_FA,
#           base_height = 8,
#           base_width = 14
#           )
```

@@

>>>>

@@

## BacDive FA profiles

```{r}
p_tax_FA <- bacdive_FA_wide %>% 
  select(-ID) %>% 
  pivot_longer(cols = -phylum, 
               names_to = "FA",
               values_to = "rel_abund") %>%
  ggplot(aes(x = FA, 
             y = rel_abund)) +
  geom_jitter(aes(color = phylum),
              size = 0.25,
              alpha = 0.3) +
  stat_pointinterval(point_interval = "median_qi",
                     alpha = 0.65) +
  facet_wrap(vars(phylum), nrow = 3) +
  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
  labs(y = "Relative Abundance (%)",
       x = "",
       color = "Phylum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1),
        panel.grid = element_blank(),
        strip.background = element_blank(),
        legend.position = "NA",
        strip.text = element_text(size = 16)
        )

cowplot::save_plot(filename = "fig_output/p_tax_FA.pdf",
          plot = p_tax_FA,
          base_height = 11,
          base_width = 9
          )
```
